Lens Modeling in \sw

### 2014-06-17 text/partA.tex
editing

\spl implements the ideas of the arrival-time surface into a modeling
program.

@@

@@

>>>>

Modelling with \spl involves three stages, markup of the image,
followed by intensive numerics in the background, followed by review
of diagnostics and possible discussion.  We now describe each of
these, at a conceptual level, without implementation details.

\subsection{Image markup}

@@

\subsection{Numerics}

@@

\subsection{Diagnostics}
